Graphical representation example: Alternative interpretations

### 2023-11-13 notebooks/Graphical_representation_alternatives.Rmd
Separates the tables with the output parameters of the orthogonal and oblique representation

The graphical representation, as computed in the draft, is:

@@

@@

```{r item-plot-out}
#| fig.cap:   Item plots in an orthogonal (left) and oblique (right) test space.
#| fig.height: 3.1
#| fig.width:  6.65
plot_orth + plot_oblique
```

And the correlation-based parameters:

```{r example-items-table-out}
#| cache: false
#| echo:  false
item_params |> select(-ends_with("_orth"))
```

@@

# Create the parameter table again:
item_params <- items_M2PL |>
  full_join(
    items_orth |> select(item:deg_2, -starts_with(COSINE_DIRTYPE)),
  )                       |>
  full_join(
    items_oblique |> select(item:deg_2, -starts_with(COSINE_DIRTYPE)),
    by     = ITEM_COLKEY,
    suffix = paste0('_', c(ORTH_SUFFIX, OBL_SUFFIX))
  )
```

```{r example-items-table-out}
```

>>>>

We first compute the original item parameters and coordinates:

@@

For reference, the MCLM version of the parameters, along with the "orthogonal"
(i.e. agnostic) ones, are:

```{r example-items-table-out}
item_params |> select(-ends_with("_obl"))
```

The graphical representation (only the oblique version is shown), as computed in
the draft, is:

@@

```{r item-plot-out}
#| fig.cap: Item plots in an oblique test space.
plot_oblique
```

And the correlation-based parameters and coordinates:

```{r example-items-obl-out}
items_oblique
```

@@

# Create the parameter table again:
item_params <- items_M2PL |> full_join(
  items_oblique |> select(item:deg_2, -starts_with(COSINE_DIRTYPE)),
  by = ITEM_COLKEY
)
```

```{r example-items-obl-out}
```
